Cross Validation Approaches for Penalized Cox Regression

### 2019-03-13 main.tex
update table 1 and figure 4

\caption{\label{Tab:sim} Simulation comparing four cross-validation methods with varying dimension and signal strength}
\centering
\begin{tabular}[t]{cccccccccc}
\toprule
 n& p& $\#$ Non-Zero & Signal & Method & $\lambda$ & log(MSE Ratio) &Brier Score & Kullback Leibler & C Index\\
\midrule
150 & 50 & 5 & low & V VH  & 0.095 (0.028) & 1.457 (0.954) & 0.242 (0.013) & 0.678 (0.029) & 0.617 (0.034) \\
    &    &   &     & Standard  & 0.087 (0.030) & 1.459 (0.922) & 0.242 (0.013) & 0.678 (0.029) & 0.618 (0.032) \\
    &    &   &     & LinearPred  & 0.088 (0.025) & 1.433 (0.927) & 0.241 (0.013) & 0.677 (0.028) & 0.620 (0.029) \\
    &    &   &     & DevResid  & 0.132 (0.032) & 1.676 (1.019) & 0.248 (0.014) & 0.689 (0.030) & 0.601 (0.044) \\
\addlinespace
150 & 50 & 5 & strong & V VH  & 0.070 (0.011) & 1.733 (0.922) & 0.177 (0.012) & 0.527 (0.030) & 0.750 (0.014) \\
    &    &   &     & Standard  & 0.066 (0.012) & 1.688 (0.909) & 0.176 (0.012) & 0.526 (0.029) & 0.749 (0.014) \\
    &    &   &     & LinearPred  & 0.067 (0.011) & 1.695 (0.925) & 0.176 (0.012) & 0.526 (0.030) & 0.750 (0.014) \\
    &    &   &     & DevResid  & 0.110 (0.012) & 2.339 (0.868) & 0.187 (0.014) & 0.554 (0.033) & 0.750 (0.018) \\
\addlinespace
300 & 10000 & 20 & low & V VH  & 0.139 (0.021) & 3.463 (0.438) & 0.244 (0.015) & 0.681 (0.032) & 0.612 (0.051) \\
    &    &   &     & Standard  & 0.105 (0.027) & 3.350 (0.458) & 0.228 (0.021) & 0.646 (0.045) & 0.639 (0.05) \\
    &    &   &     & LinearPred  & 0.107 (0.026) & 3.360 (0.462) & 0.229 (0.021) & 0.648 (0.045) & 0.638 (0.049) \\
    &    &   &     & DevResid  & 0.139 (0.027) & 3.454 (0.447) & 0.243 (0.018) & 0.678 (0.038) & 0.610 (0.058) \\
\addlinespace
500 & 10000 & 20 & strong & V VH  & 0.072 (0.005) & 3.469 (0.480) & 0.162 (0.015) & 0.495 (0.036) & 0.784 (0.021) \\
    &    &   &     & Standard  & 0.056 (0.005) & 3.174 (0.504) & 0.153 (0.011) & 0.465 (0.029) & 0.782 (0.017) \\
    &    &   &     & LinearPred  & 0.057 (0.005) & 3.204 (0.498) & 0.153 (0.011) & 0.466 (0.029) & 0.783 (0.017) \\
    &    &   &     & DevResid  & 0.076 (0.005) & 3.545 (0.467) & 0.167 (0.015) & 0.508 (0.035) & 0.782 (0.022) \\
\bottomrule
\end{tabular}
\end{table}

@@

\subsection {Stability}
\label{Sec:stability}

\par In this section, we present a small simulation study to illustrate the numerical stability issues faced by standard cross-validation in the partial likelihood setting.  The standard approach is both straightforward and enjoys very good predictive accuracy, as seen in Section~\ref{Sec:accuracy}. The main drawback to its widespread use is that the number of uncensored observations in the test set may be insufficient to construct a well-defined partial likelihood, leaving the overall estimate of cross-validation error undefined as well.

@@

\subsection {Leave-One-Out Cross Validation \bnote{Updating Simulation}}
\label{Sec:loocv}

As discussed earlier, standard cross-validation cannot be used to carry out leave-one-out cross validation (LOOCV) for Cox regression models.  The three other approaches (V\&VH, linear predictor, and deviance residual), however, are not subject to the stability issues described in Section~\ref{Sec:stability}, and can be used to implement LOOCV.  Here, we compare these three approaches for carrying out LOOCV, and also compare LOOCV to 10-fold CV.

@@

\begin{figure}[h]
  \centering
  \includegraphics[height= 8cm ]{./figures/figure_4.png}
  \caption{\label{Fig:loocv}LOOCV\note{Needs a better caption; also, should y-axis be log mse ratio?}}
\end{figure}

>>>>

\caption{\label{Tab:sim} Simulation comparing four cross-validation methods with varying dimension and signal strength}
\centering
\begin{tabular}[t]{cccccccccc}
\toprule
 n& p& $\#$ Non-Zero & Signal & Method & $\lambda$ & log(MSE Ratio) &Brier Score & Kullback Leibler & C Index\\
\midrule
150 & 50 & 5 & weak & V VH  & 0.098 (0.030) & 1.561 (0.851) & 0.245 (0.014) & 0.685 (0.030) & 0.610 (0.035) \\
    &    &   &     & Standard  & 0.088 (0.025) & 1.531 (0.838) & 0.244 (0.013) & 0.683 (0.029) & 0.614 (0.029) \\
    &    &   &     & LinearPred  & 0.092 (0.029) & 1.543 (0.846) & 0.245 (0.014) & 0.684 (0.030) & 0.612 (0.034) \\
    &    &   &     & DevResid  & 0.098 (0.029) & 1.547 (0.848) & 0.245 (0.014) & 0.684 (0.030) & 0.611 (0.035) \\
\addlinespace
150 & 50 & 5 & strong & V VH  & 0.071 (0.010) & 1.586 (0.989) & 0.176 (0.011) & 0.526 (0.027) & 0.750 (0.012) \\
    &    &   &     & Standard  & 0.066 (0.011) & 1.544 (0.971) & 0.176 (0.011) & 0.526 (0.028) & 0.749 (0.013) \\
    &    &   &     & LinearPred  & 0.067 (0.010) & 1.540 (0.981) & 0.176 (0.011) & 0.525 (0.028) & 0.750 (0.012) \\
    &    &   &     & DevResid  & 0.094 (0.011) & 1.995 (0.841) & 0.181 (0.011) & 0.539 (0.026) & 0.751 (0.013) \\
\addlinespace
400 & 10000 & 20 & weak & V VH  & 0.126 (0.019) & 2.958 (0.416) & 0.251 (0.012) & 0.696 (0.026) & 0.589 (0.044) \\
    &    &   &     & Standard  & 0.103 (0.022) & 2.880 (0.437) & 0.244 (0.015) & 0.680 (0.031) & 0.603 (0.039) \\
    &    &   &     & LinearPred  & 0.105 (0.023) & 2.886 (0.437) & 0.244 (0.015) & 0.681 (0.031) & 0.602 (0.039) \\
    &    &   &     & DevResid  & 0.107 (0.022) & 2.895 (0.433) & 0.245 (0.014) & 0.683 (0.03) & 0.602 (0.039) \\
\addlinespace
400 & 10000 & 20 & strong & V VH  & 0.084 (0.012) & 3.799 (0.548) & 0.176 (0.03) & 0.528 (0.069) & 0.763 (0.048) \\
    &    &   &     & Standard  & 0.059 (0.007) & 3.455 (0.578) & 0.154 (0.019) & 0.468 (0.049) & 0.780 (0.031) \\
    &    &   &     & LinearPred  & 0.060 (0.007) & 3.479 (0.574) & 0.155 (0.019) & 0.470 (0.049) & 0.780 (0.030) \\
    &    &   &     & DevResid  & 0.076 (0.018) & 3.708 (0.518) & 0.166 (0.024) & 0.502 (0.057) & 0.772 (0.049) \\
\bottomrule
\end{tabular}
\end{table}

@@

\subsection {Stability}
\label{Sec:stability}
  \bnote{still working on a new simulation}
\par In this section, we present a small simulation study to illustrate the numerical stability issues faced by standard cross-validation in the partial likelihood setting.  The standard approach is both straightforward and enjoys very good predictive accuracy, as seen in Section~\ref{Sec:accuracy}. The main drawback to its widespread use is that the number of uncensored observations in the test set may be insufficient to construct a well-defined partial likelihood, leaving the overall estimate of cross-validation error undefined as well.

@@

\subsection {Leave-One-Out Cross Validation}
\label{Sec:loocv}

\bnote{Simulation Updated, still need to work on writing}
As discussed earlier, standard cross-validation cannot be used to carry out leave-one-out cross validation (LOOCV) for Cox regression models.  The three other approaches (V\&VH, linear predictor, and deviance residual), however, are not subject to the stability issues described in Section~\ref{Sec:stability}, and can be used to implement LOOCV.  Here, we compare these three approaches for carrying out LOOCV, and also compare LOOCV to 10-fold CV.

@@

\begin{figure}[h]
  \centering
  \includegraphics[height= 8cm ]{./manuscript_figure/figure_4.png}
  \caption{\label{Fig:loocv}LOOCV\note{Needs a better caption; also, should y-axis be log mse ratio?}}
\end{figure}
